Spikes demo

### 2018-11-06 analysis/spikesdemo.Rmd
wflow_publish("spikesdemo.Rmd")

```{r install-pkgs-2, eval=FALSE}
library(devtools)
install_github("stephens999/ashr",upgrade_dependencies = FALSE,
               build_vignettes = TRUE)
install_github("stephenslab/smashr",upgrade_dependencies = FALSE,
               build_vignettes = TRUE)
```

@@

We begin by loading the ashr, smashr, scales, ggplot2 and cowplot
packages, as well as some additional functions used in the code below.

```{r load-pkgs, warning=FALSE, message=FALSE}
library(ashr)
library(smashr)
library(scales)
library(ggplot2)
library(cowplot)
source("../code/misc.R")
```

@@

Simulate the noisy observations from the normal distribution with
means that are given by the "spikes" function, and with
spatially-structured variances given by the "clipped blocks" function.

@@

```{r plot-simulated-data, fig.height=5, fig.width=10}
par(cex.axis = 1,cex.lab = 1.25)
plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
     ylab = "",lwd = 1.7,xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.sp + 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
lines(mu.sp - 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
points(x.sim,cex = 0.7,pch = 16,col = "darkblue")
```

This plot shows the "spikes" mean function (the black line), +/- 2
standard deviations (the orange lines), and the simulated data (the
blue points).

>>>>

```{r install-pkgs-2, eval=FALSE}
library(devtools)
install_github("stephens999/ashr",upgrade_dependencies = FALSE)
install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
```

See the "Session Info" at the bottom of this example for the versions
of the software and R packages that were used to generate the results
shown below.

@@

We begin by loading the ashr, smashr, ggplot2 and cowplot packages, as
well as some additional functions used in the code below.

```{r load-pkgs, warning=FALSE, message=FALSE}
library(ashr)
library(smashr)
library(ggplot2)
library(cowplot)
source("../code/misc.R")
```

@@

Simulate the noisy observations from the normal distribution with
means that are given by the "Spikes" function, and with
spatially structured variances given by the "Clipped Blocks" function.

@@

```{r plot-simulated-data, fig.height=5, fig.width=10}
par(cex.axis = 1,cex.lab = 1.25)
plot(mu.sp,type = 'l',ylim = c(-0.05,1),xlab = "position",
     ylab = "",lwd = 2,xaxp = c(0,1024,4),yaxp = c(0,1,4))
lines(mu.sp + 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
lines(mu.sp - 2*sig.cb,col = "darkorange",lty = 5,lwd = 1.8)
points(x.sim,cex = 0.7,pch = 16,col = "dodgerblue")
```

This plot shows the "spikes" mean function (the black line), +/- 2
standard deviations (the orange lines), and the simulated data (the
light blue points).
